Commutative Character Sheaves

### 2015-11-17 followup.tex
Commit for talking . . .

A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
One of the main results of \cite{yu:models} is that there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that $\,^\circ K = \underline{G}(\OK)$ \cite{yu:models}*{Prop 10.2}.
As explained in \cite{yu:models}*{\S 10.4}, the
the group scheme $\underline{G}$ comes with the following auxillary data:
\begin{enumerate}
\item
	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\prod_{i=0}^d \underline{J}^i(\OK) = \underline{G}(\OK),\] where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$, and such that $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, for $j=1, \ldots, d$;
\item affine smooth group schemes $\underline{G}^{j}$, for $j=1, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
\[
\underline{G}^{j}(\OK) = \prod_{i=0}^{j} \underline{J}^i(\OK),
\] 
where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$ and $\underline{G}^{j}(\OK)$ with its image under $\underline{G}^j \to \underline{G}$.
\end{enumerate}

The representation $\,^\circ \rho$ of $\underline{G}(\OK)$ is build from the following data, as explained in \cite{yu:models}*{\S 10.5}:
\begin{enumerate}
\item
	a representation $\sigma$ of $\underline{G}_s\red(\Fq)$;
\item
for $j=1,\ldots, d-1$, 
\begin{enumerate}
\item
a representation $\eta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^i$,
\item
a representation $\epsilon_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$
\item
a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$, for $j=1,\ldots, d$;
\end{enumerate}
\item
	a linear quasicharacter $\tau_d$ of $\underline{G}(\OK)$.
\end{enumerate}
From this data, the representation $\,^\circ \rho$ is built as follows.
\begin{enumerate}
\item 
	Let $\tau_0$ be the representation of $\underline{G}(\OK)$ obtained by pulling back $\sigma$ along 
\[\underline{G}(\OK) \to \underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq).\]
\item For $j=1,\ldots, d-1$, 
\begin{enumerate}
\item
	Let $\dot{\eta}_j$ be the representation of $\underline{J}^j(\OK)$ obtained by pulling back $\eta_j$ along 
\[\underline{J}^{j}(\OK) \to \underline{J}^{j}_s(\Fq) \to H^j(\Fq),\]
for $j=1,\ldots, d-1$.
\item 
	Let $\dot{\epsilon}_j$ be the representation of $\underline{G}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
\[\underline{G}^{j-1}(\OK) \to \underline{G}^{j-1}_s(\Fq) \to (\underline{G}^{j-1})_s\red(\Fq),\]
for $j=1,\ldots, d-1$.
\item
	Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, consider the representation 
\[
	(\phi_{j-1}\otimes \dot{\epsilon}_j)\times \dot{\eta}_j
\]
 of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$. 
	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\tau_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$. 
\end{enumerate}
\item
	Then $\,^\circ \rho = \tau_0 \otimes \cdots \tau_d$.
\end{enumerate}

@@

Introduce morphisms $\underline{G}\to \underline{M}^j$ and $\underline{M}^{j} \to \underline{M}^{j-1}$ and $\underline{M}^j \to \underline{J}^j$.
\[
\begin{tikzcd}
\underline{J}^j \arrow{r} & \underline{G}^{j} \arrow{r} 
& \underline{G} \arrow{r}  
& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
& \arrow{u} \underline{G}^{j-1} 
&
& \underline{M}^{j-1}
&
\end{tikzcd}
\]
Interpret 
\begin{enumerate}
\item
	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
\item
	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
\end{enumerate}
so that
\begin{enumerate}
\item 
	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
for $j=1,\ldots, d-1$.
\item
	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
\item
	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$. 
\end{enumerate}

\[
\begin{tikzcd}
\underline{G} \arrow{r}  
& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
\underline{G}_s \arrow{u} \arrow{d}
& \underline{M}^{j-1}
 & (\underline{J}^j)_s \arrow{u} \arrow{d} \\
\underline{G}_s\red & (\underline{M}^{j-1})_s \arrow{u} \arrow{d} & H^j \\
& (\underline{M}^{j-1})_s\red & 
\end{tikzcd}
\]

Now, we introduce the tools needed to geometrize all the ingredient representations.
\begin{enumerate}
\item
Let $(A_0,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$, in the sense of [Lusztig].
Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
\item For $j=1,\ldots, d-1$, 
\begin{enumerate}
\item
Let $(B_0^{j},\varphi)$ be a Frobenius-stable character sheaf on $H^j$ in the sense of [Boyarchenko].
Let $(B^{j},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{J}^j_s$ obtained by pull-back.
\item
Let $(C_0^{j-1},\varphi)$ be a Frobenius-stable character sheaf on $(\underline{M}^{j-1})_s\red$ in the sense of [Lusztig].
Let $(C^{j-1},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{M}^{j-1}_s$ obtained by pull-back.
\item
Let $\cs{E}_n$ be a commutative quasicharacter sheaf on $M_n^{j-1}$.
\end{enumerate}
\item
Let $\cs{L}_n$ be a commutative quasicharacter sheaf on $G_n$.
\end{enumerate}
\[
\begin{tikzcd}
G \arrow{r}  \arrow{d}
& M^{j} \arrow{r} \arrow{d}
& J^j \arrow{d} \\
G_n \arrow{r}  \arrow{d}
& M_n^{j} \arrow{r} \arrow{d}
& J_n^j \arrow{d} \\
\underline{G}_s \arrow{d}
& \underline{M}^{j-1} \arrow{d}
& (\underline{J}^j)_s  \arrow{d} \\
\underline{G}_s\red 
& (\underline{M}^{j-1})_s \arrow{d} & H^j \\
& (\underline{M}^{j-1})_s\red 
& 
\end{tikzcd}
\]

We may now encorporate all these ingredients into one sheaf on $G_n$.
\begin{enumerate}
\item
Let $\cs{A}_n$ be sheaf on $G_n$ produced from $A$ by pullback along $G_n \to \underline{G}_s$.
\item
For $j=1, \ldots, d-1$,
\begin{enumerate}
\item let $\cs{B}^j$ be the sheaf on $M^j_n$ ...
\item let $\cs{C}^j$ be the sheaf on $M^j_n$ ...
\item let $\cs{E}^j$ be the sheaf on $M^j_n$ ...
\end{enumerate}
\item Let $\cs{L}$ be the sheaf on $G_n$ as above...
\end{enumerate}
Combine: $B$, $C$ and $E$ into $D$
\[
\cs{A} \otimes \cs{D}^1 \otimes \cdots \otimes \cs{D}^{d-1} \otimes \cs{L}.
\]

>>>>

A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
One of the main results of \cite{yu:models} is that there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that $\,^\circ K = \underline{G}(\OK)$ \cite{yu:models}*{Prop 10.2}.
As explained in \cite{yu:models}*{\S 10.4}, the
the group scheme $\underline{G}$ comes with the following auxillary data:
\begin{enumerate}
\item[(Ji)]
	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\prod_{i=0}^d \underline{J}^i(\OK) = \underline{G}(\OK),\] where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$, and such that $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, for $j=1, \ldots, d$;
\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=1, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
\[
\underline{G}^{j}(\OK) = \prod_{i=0}^{j} \underline{J}^i(\OK),
\] 
where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$ and $\underline{G}^{j}(\OK)$ with its image under $\underline{G}^j \to \underline{G}$.
\end{enumerate}

The representation $\,^\circ \rho$ of $\underline{G}(\OK)$ is build from the following data:
\begin{enumerate}
\item
	a representation $\sigma$ of $\underline{G}_s\red(\Fq)$;
\item
if $d \geq 2$, for $j=1,\ldots, d-1$, 
\begin{enumerate}
\item
a representation $\beta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^j$,
\item
a representation $\kappa_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$
\item
a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$;
\end{enumerate}
\item
	a linear quasicharacter $\phi$ of $\underline{G}(\OK)$.
\end{enumerate}
From this data, the representation $\,^\circ \rho$ is built as follows, as explained in \cite{yu:models}*{\S 10.5}.
\begin{enumerate}
\item 
	Let $\dot{\sigma}$ be the representation of $\underline{G}_s(\Fq)$ obtained by pulling back $\sigma$ along $\underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq)$. 	
	Let $\ddot{\sigma}$ be the representation of $\underline{G}(\OK)$ obtained by pullback along $\underline{G}(\OK) \to \underline{G}_s(\Fq)$.
\item For $j=1,\ldots, d-1$, 
\begin{enumerate}
\item
	let $\dot{\beta}_j$ be the representation of $\underline{J}^{j}_s(\Fq)$ obtained by pulling back $\beta_j$ along $\underline{J}^{j}_s(\Fq) \to H^j(\Fq)$ and let $\ddot{\beta}_j$ be . . . 
;
\item 
	let $\dot{\kappa}_j$ be the representation of $\underline{G}^{j-1}_s(\Fq)$ obtained by pulling back $\kappa_j$ along $\underline{G}^{j-1}_s(\Fq) \to (\underline{G}^{j-1})_s\red(\Fq)$ and let $\ddot{\kappa}_j$ . . ;
\item
	let $\phi_{j-1}$ be the linear quasicharacter of $\underline{G}^{j-1}(\OK)$ as above. 
\end{enumerate}
\item Let $\phi$ be the linear quasicharacter of $\underline{G}(\OK)$, as above.
\end{enumerate}
Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, combine $\ddot{\beta}_j$, $\ddot{\kappa}_j$  and $\phi_j$ to form the representation $(\phi_{j-1}\otimes \ddot{\kappa}_j)\times \ddot{\beta}_j$ of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$. 
	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\delta_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$.
Then 
\[
\,^\circ \rho = \ddot{\sigma} \otimes \delta_1 \cdots \otimes \delta_{d-1} \otimes \phi.
\]

@@

Introduce morphisms $\underline{G}\to \underline{M}^j$ and $\underline{M}^{j} \to \underline{M}^{j-1}$ and $\underline{M}^j \to \underline{J}^j$.
\[
\begin{tikzcd}
\underline{J}^j \arrow{r} & \underline{G}^{j} \arrow{r} 
& \underline{G} \arrow{r}  
& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
& \arrow{u} \underline{G}^{j-1} 
&
& \underline{M}^{j-1}
&
\end{tikzcd}
\]
\[
\begin{tikzcd}
\underline{G} \arrow{r}  
& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
\underline{G}_s \arrow{u} \arrow{d}
& \underline{M}^{j-1}
 & (\underline{J}^j)_s \arrow{u} \arrow{d} \\
\underline{G}_s\red & (\underline{M}^{j-1})_s \arrow{u} \arrow{d} & H^j \\
& (\underline{M}^{j-1})_s\red & 
\end{tikzcd}
\]

Now, we introduce the tools needed to geometrize all the ingredient representations.
\begin{enumerate}
\item
Let $(A_0,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$, in the sense of [Lusztig].
Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
\item For $j=1,\ldots, d-1$, 
\begin{enumerate}
\item
Let $(B_0^{j},\varphi)$ be a Frobenius-stable character sheaf on $H^j$ in the sense of [Boyarchenko].
Let $(B^{j},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{J}^j_s$ obtained by pull-back.
\item
Let $(C_0^{j-1},\varphi)$ be a Frobenius-stable character sheaf on $(\underline{M}^{j-1})_s\red$ in the sense of [Lusztig].
Let $(C^{j-1},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{M}^{j-1}_s$ obtained by pull-back.
\item
Let $\cs{E}_n$ be a commutative quasicharacter sheaf on $M_n^{j-1}$.
\end{enumerate}
\item
Let $\cs{L}_n$ be a commutative quasicharacter sheaf on $G_n$.
\end{enumerate}
\[
\begin{tikzcd}
G \arrow{r}  \arrow{d}
& M^{j} \arrow{r} \arrow{d}
& J^j \arrow{d} \\
G_n \arrow{r}  \arrow{d}
& M_n^{j} \arrow{r} \arrow{d}
& J_n^j \arrow{d} \\
\underline{G}_s \arrow{d}
& M_n^{j-1} \arrow{d}
& (\underline{J}^j)_s  \arrow{d} \\
\underline{G}_s\red 
& (\underline{M}^{j-1})_s \arrow{d} & H^j \\
& (\underline{M}^{j-1})_s\red 
& 
\end{tikzcd}
\]

We may now encorporate all these ingredients into one sheaf on $G_n$.
\begin{enumerate}
\item
Let $\cs{A}_n$ be sheaf on $G_n$ produced from $A$ by pullback along $G_n \to \underline{G}_s$.
\item
For $j=1, \ldots, d-1$,
\begin{enumerate}
\item let $\cs{B}^j$ be the sheaf on $J^j_n$ ...
\item let $\cs{C}^j$ be the sheaf on $M^{j-1}_n$ ...
\item let $\cs{L}^j$ be the sheaf on $M^{j-1}_n$ ...
\end{enumerate}
Combine: $\cs{B}^j$, $\cs{C}^j$ and $\cs{E}^j$ into $\cs{D}^j$ on $G_n$ . . . .
\item Let $\cs{L}$ be the sheaf on $G_n$ as above...
\end{enumerate}

\[
\cs{A} \otimes \cs{D}^1 \otimes \cdots \otimes \cs{D}^{d-1} \otimes \cs{L}.
\]

Interpret 
\begin{enumerate}
\item
	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
\item
	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
\end{enumerate}
so that
\begin{enumerate}
\item 
	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
for $j=1,\ldots, d-1$.
\item
	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
\item
	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$. 
\end{enumerate}
